Asymptotic Validity of the Bayes-Inspired Indifference Zone Procedure: the Non-Normal Known Variance Case

### 2015-06-10 montreal/presentation.tex
presentation

@@

\begin{itemize}
\item BIZ is an elimination procedure that does not use Bonferroni's inequality.
\\
\textrm{}\\
\item Its lower bound on worst-case probability of correct selection in
the preference zone is tight in continuous time, and almost tight
in the discrete time.\\
\textrm{}\\
\item The number of samples required by BIZ is significantly smaller than
the KN procedure and the $\mathscr{P}_{B}^{*}$ procedure.\\
\textrm{}\\
\item It satisfies the IZ guarantee under the follwing assumptions:

@@

\item Variances are either common across alternatives, or have an integer
multiple structure. 
\end{itemize}
\end{itemize}
\end{block}
\end{frame}

@@

>>>>

\begin{frame}{Conservatism Causes the Number of Samples Taken to Be Larger than
Necessary }

\begin{itemize}
\item A user wants to meet the IZ guarantee and have $\mathbb{E}\left[\mbox{\# of samples}\right]$
as small as possible.\\
\textrm{}\\
\item The conservatism can be defined as $\mbox{PCS}\left(\mu\right)-P^{*}$.
If this number is large, then $\mathbb{E}\left[\mbox{sample size}\right]$
may be large. 
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Sources of Conservatism}

\begin{itemize}
\item The change from discrete time to continuous time often used to show
IZ guarantees.\\
\textrm{}\\
\item The configuration under consideration is not a worst-case configuration.
\\
\textrm{}\\
\item Bonferroni\textquoteright s inequality.
\end{itemize}
\end{block}
\end{frame}

@@

\begin{itemize}
\item BIZ is an elimination procedure that eliminates the use of Bonferroni\textquoteright s
inequality, reducing conservatism. \\
\textrm{}\\
\item Its lower bound on worst-case probability of correct selection in
the preference zone is tight in continuous time, and almost tight
in the discrete time.\\
\textrm{}\\
\item The number of samples required by BIZ is significantly smaller than
the KN procedure and the $\mathscr{P}_{B}^{*}$ procedure.\\
\textrm{}\\

\end{itemize}
\end{block}
\end{frame}

\begin{frame}{BIZ Requires Fewer Samples}
\begin{figure}[ht]
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{BIZ.png}
\end{figure}
\end{frame}

\begin{itemize}
\item It satisfies the IZ guarantee under the following assumptions:

@@

\item Variances are either common across alternatives, or have an integer
multiple structure.\\
\textrm{}\\
\end{itemize}
\item Based on empirical evidence, the BIZ procedure satisfies the IZ guarantee
almost always even when the last two assumptions are not true.\\
\textrm{}\\
\item Our contribution is to theoretically explain why it works. Specifically,
we show asymptotic validity of the BIZ procedure. 
\end{itemize}
\end{block}
\end{frame}

@@

\begin{frame}{Conclusion}

\begin{itemize}
\item BIZ is a fully sequential IZ procedure with elimination that eliminates
one common source of conservatism: Bonferroni's inequality.\\
\textrm{}\\
\item We have proved the asymptotic validity of the Bayes-inspired Zone
procedure when the variances are known. This implies that BIZ procedure
satisfies the IZ guarantee when the means of the systems are very
similar. \\
\textrm{}\\
\item Theoretical results require unrealistic assumptions on the sampling
variances, but empirical results suggest that behavior is robust to
violations of these assumptions in the problem regimes tested.\\
\textrm{}\\
\end{itemize}
\end{block}

\end{frame}

\begin{frame}{Future Work}

\begin{itemize}
\item Asymptotic validity when the variances are unknown.\\
\textrm{}\\
\item Probability of good selection guarantee: 
\begin{eqnarray*}
\forall\mu,\mbox{ PGS}\left(\mu\right):=\mathbb{P}\left(\mu_{k}-\mu_{\hat{x}}\leq\delta\right) & \geq & P^{*}
\end{eqnarray*}
 \\
\textrm{}\\
\end{itemize}
\end{block}
\end{frame}
